% ===================== CV IN LaTeX (moderncv) =====================
\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2.8cm}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% ---------------------- Personal Data -----------------------------
\name{Eduardo Antunes}{Duda}
\address{Porto Alegre, RS}{Brazil}{}
\phone[mobile]{(+55) 51 99583-4030}
\email{eduardo.dudaa@hotmail.com}
\social[linkedin]{linkedin.com/in/eduardo-antunes-duda-26b10b160}

\begin{document}

% Ensure the title is created without compilation errors
\makecvtitle

% -------------------------- Summary -------------------------------
\section{Summary}
\cvitem{}{Bla bla.}

% ------------------------ Work Experience -------------------------
\section{Work Experience}
\cventry{Aug 2025 -- Current}{Master's student}{Laboratório de Metalurgia Física (LAMEF) -- UFRGS}{Porto Alegre}{}{Research on corrosion, mechanical properties on aluminium alloys.}

% ------------------------- Education ------------------------------
\section{Education}
\cventry{2020 -- 2025}{Bachelor in Materials Engineering}{Universidade Federal do Rio Grande do Sul (UFRGS)}{Porto Alegre}{}{Thesis on Insights into the corrosion behavior to AA5083 multi-layer friction surfacing deposits in chloride solutions.}

% ------------------------- Languages ------------------------------
\section{Languages}
\cvitem{Portuguese}{Native}
\cvitem{English}{Fluent (B2 CEFT)}
\cvitem{Spanish}{Intermediate}
\cvitem{German}{Intermediate (A1)}

% ------------------------- Publications ---------------------------
\section{Publications}
\cvitem{2024}{Antunes Duda, E., Kallien, Z., da Silva Soares, S., Hernandez Schneider, T., Ribeiro Piaggio Cardoso, H., Vieira Braga Lemos, G., \& Klusemann, B. Corrosion behavior of multi-layer friction surfaced structure from dissimilar aluminum alloys. \emph{Scientific Reports}, 14(1), 9882.}
\cvitem{2022}{Duda, E. A., da Silva Soares, S., Buzzatti, D. T., Lemos, G. V. B., Schneider, T. H., Cardoso, H. R. P., \& Reguly, A. An investigation on galvanic corrosion in friction stir welded AA 5083 aluminum alloy. \emph{Tecnologia em Metalurgia, Materiais e Mineração}, 19, 0--0.}
\cvitem{2024}{Hoffmann, M., Kallien, Z., Duda, E. A., \& Klusemann, B. Insight into layer formation during friction surfacing: Relationship between deposition behavior and microstructure. \emph{Materials Today Communications}, 41, 110337.}
\cvitem{2025}{Hoffmann, M., Duda, E. A., Aspes, P., \& Klusemann, B. Effect of ambient conditions in friction surfacing. \emph{Welding in the World}, 69(2), 397--406.}

% ------------------------- Additional Training --------------------
\section{Additional Training}
\cvitem{2021}{Fire Prevention and Fighting Training, LAMEF -- UFRGS, Brazil}


% ---------------------- Volunteer Activities ----------------------
\section{Volunteer Activities}
\cvitem{2016 -- 2018}{\textbf{Rotaract Itapema} -- Co-founder; conducted philanthropic activities with Lions Club of Balneário Camboriú/SC in Brazil for underprivileged communities in the region.}

% ------------------------- Skills --------------------------------
\section{Skills}
\cvitem{}{Microsoft Office}

\end{document}
